\section{Nonfunctional Requirements}

The user will be able to access social media integrated applications, and decide whether
or not to keep their social media profile updated and informed with updates on progress from
their fantasy league. (ST-15) They may also receive email updates with various progressions in
the game (ST-14)\\

The user will be kept updated on the progress of other users to view their trades as well as
recent market trades and trends. (ST-12, ST-11)\\

Users will also have access to on-site term explanation similar to that seen on Wikipedia.
That is, they may scroll over an underlined term to find a brief definition and additional
resources. (ST-10)\\


\subsection{Functionality}
Additional features for security will be enabled through the use of a
OpenID and OAuth through a third-party library. There exists several packages
for the purpose of authentication and authorization of users. Key authentication
features are the ability to encrypt and store passwords, provide recovery
options for users that have forgotten their password, and store a cookie to
validate the session.


\subsection{Usability}
A key point in the design of this application is ease of use and appeal to the
users. The application should be interactive, informative and consistent across
multiple platform paradigms. Additionally the application will be used to
provide the educational interfaces noted in ST-9 which should be able to be
toggled on and off so that users can always view the information again.


\subsection{Reliability}
In order to ensure that there is no confusion to the user in the case of the
internet or server failure, all transactions end with a final confirmation, and
no changes to the account are made until after this confirmation. The user's
portfolio will thus always be in a consistent state and will be restored when
the user is able to log back in. A user that leaves the application and returns
later will still be logged in. Server failure should also be dealt with by
keeping backups of user data.  Proper care should also be taken to handle a
situation where a particular stock source is not available (i.e. Yahoo Finance).


\subsection{Performance}
In order to have a great performance, the website should be as lightweight as
possible by keeping hardware demands to a minimum on both the client and server
sides. For it to be efficient, any task initiated by the user should be
completed in a timely manner. The web server should be able to serve concurrent
requests especially when a large number of users are logged in. Any frameworks
used should be lightweight but consideration should be taken not to prematurely
optimize.


\subsection{Supportability}
It should be feasible to extend pr update any server components and include
improved versions of modules which can be installed only by administrators. For
scaling purposes, it should be made easy to include an additional number of
servers to achieve load balancing. The system should be platform independent so
that it is easy to move to newer technologies or the next versions of web
server. The system itself should also be backed up to a remote server for the
sole purpose of extending functionality and testing new features in a
controlled environment.

