\section{Glossary of Terms}

{
\setlength{\parindent}{0cm}
\textbf{Achievement} -- Any set goal reached by an investor.
Achievement rewards can be managed by a league manager and
may include badges, capital, equity, etc.\\

\textbf{Transaction Ticker} -- Constantly updating scroll of
most recent trades across the market. Users can observe market
trends from global equities which may or may not already be
in their portfolio.\\

\textbf{Leaderboard} -- Global or league based ranking system
determined by overall net worth of player.\\

\textbf{Security} -- A tradable asset of any kind. Can include
debts, equities, or derivatives. For the purpose of this game,
we will be dealing primarily with equities.\newline

\textbf{Dividend} -- A payment made by a corporation to its
shareholders, generally as a distribution of profit. It is
usually distributed as a fixed percent of shareholder value.\\

\textbf{Derivative} -- Any financial contract which derives its
value from another asset or index.\\

\textbf{Option} -- Gives the user the option to buy or sell an
asset at a specified price on or before a given date. The buyer
and seller are both obligated to fulfill the transaction on the
given date if the option is taken.\\

\textbf{Future} - Allows the buyer to buy an asset at its current
price and pay for it at that price in the future. A future is
generally exchange traded. The buyer and seller are both obligated
to fulfill the transaction on the given date if the future is taken.\\

\textbf{Forward} -- Allows the buyer to buy an asset at its current
price and pay for it at that price in the future. A forward is a
private agreement between buyer and seller not necessarily based around
market equity. The buyer and seller are both obligated to fulfill
the transaction on the given date if the future is taken.\\

\textbf{League} -- A market simulation with a pre-determined rule set
and several investors with a common goal to determine a winner. Goals
can vary across leagues as determined by league managers. Investors can
choose to opt into a private league, public league, or no league at all.\\

\textbf{Portfolio} -- A detailed account of assets associated with a
particular investor in a given league. Portfolios are unique to each user
and will contain specific details such as earnings, losses, performance,
averages, as well as detailed asset performances of equities within the
given portfolio.\\

\textbf{League manager} -- The league manager will have the responsibility
of added and/or removing investors from the league. League managers
control settings, and victory conditions for a particular league. League
managers maintain their manager status only for the league in which they
have created.\\

\textbf{Order} -- An investor must place an order for the purchase or
sale of an asset.\\

\textbf{Stock} -- A type of asset that represents equity in a company.
\begin{itemize}
    \item \textbf{Ask Price} -- The price at which a trader is willing
                                to sell a stock.
    \item \textbf{Bid Price} -- The price a trader is willing to pay for
                                a stock.
    \item \textbf{Bid-Ask Spread} -- The bid-ask spread describes the
                                     difference in price between the bid
                                     and the ask. These two prices are
                                     marginally different, but always with
                                     the ask being the more expensive of the
                                     two. It represents the friction inherent
                                     in trading a stock.
\end{itemize}

\textbf{Ticker Symbol} -- an abbreviation used to uniquely identify publicly
traded shares of a particular stock on a particular stock market.\\

\textbf{Symbol List} -- a list of a market/several market's ticker symbols.\\


\textbf{Market Order} -- Any order placed for immediate market transaction.\\

\textbf{Buy} -- User has elected to purchase a particular stock and has placed
a bid for that stock.\\

\textbf{Sell} -- User has elected to sell a particular stock and has posted an
ask price for it.\\

\textbf{Short Order} -- Typically used by an investor who expects the value of
a stock to decrease. The investors borrows shares of a particular stock and sells
them at market price. The investor is responsible for the increased value as well
should the stock's value increase.\\

\textbf{Limit} - An investment which will only take place at a given price. An
investor placing a buy limit will place a maximum amount the pay and an investor
place a sell limit will place a minimum value for which the stock be sold. Limit
orders are not guaranteed to ever process, and only do when the particular limit
is reached.\\

\textbf{Stop} -- Orders which are activated if a particular stop falls below or
rises above a particular price. It is used to minimize gains and losses for the
investor.\\

\textbf{Share} -- A small percentage of a given company which can purchased or
sold from other traders.\\
}
