\section{Hardware Requirements}

The hardware requirements on the server side are the main
contribution to the operation of Paramount Investments League,
leaving the client-side with minimal requirements. In fact,
the only requirement of a client will that it runs a browser
that is capable of running a modern web browswer.

\subsection{Internet Connection}

In order for Paramount Investments League to use any of its core
functions (trading stocks, updating user portfolio, tracking
administrative actions, etc.), an internet connection is required.
Since most of the data being transferred is text (executable
instructions), a low band of frequency is required. Note that a
complete scalable analysis has not been performed on the system,
so a low band of frequency is based off of the needs of the current
website. For ideal performance, higher bandwidths of frequency
should be used in order to reduce any overhead. A network
connection between the server and the Yahoo Finance API is necessary
during trade hours (9:30am - 4:00pm Monday through Friday), otherwise,
no investors can perform a transaction.

\subsection{Disk Space}

The server must have adequate hard drive space to be able to
store all of the database information. All data being stored
is the sum of all program instructions for the system. 10 GB
of storage space should be sufficient for the system.

\subsection{System Memory}

Since this system is in active development, there is limited
concrete evidence that supports the overall performance of the
system. The system will load copies of database stored information
in order to operate over it. For better throughput, the memory
should be managed using a Least Recently Used scheme (LRU) in
order to keep the system memory populated with useful information.
A LRU scheme will release any bits of memory that haven’t been
accessed in a long time, and it will replace it with information
that is used more often. Also, any operations used on loaded
information will also use up system memory. A minimum of 512 MB
should be used for testing our system. In addition, as our user
based expands, it is obvious that the system memory will also
have to grow with it.

\subsection{Client-side Hardware Requirements}

The core hardware requirement on the client-side of the system
will be an internet connection. This is essential for the client
to be able to remotely connect to the server in order to access
the database. Without an internet connection, no client will be
able to use a web browser to visit the Paramount Investments League
website. In addition to an internet connection, and for a friendly
user experience, anyone on the client-side should have a functional
mouse and keyboard, as well as a graphic display to see their
portfolio. To display the Paramount Investments League website,
a screen with a minimum resolution of 800x600 pixels is adequate.


