
\subsection{Investor}
A user who has an account in our servers and is logged in to their account. These will be regarded as our primary stakeholders.\cite{wiki:Stakeholder}
\begin{itemize}
\item[--] Research the latest updates in the market
\item[--] View their portfolio
\item[--] Execute orders of any kind
\item[--] Join/create a league
\item[--] Take part in competitions
\end{itemize}

\subsection{Guest}
A visitor to the website who has either not logged in or just a simple visitor. Visitors will be regarded as secondary stakeholders.\cite{wiki:Stakeholder}
\begin{itemize}
\item[--] Register and create an account using OpenID/OAuth2
\item[--] View the latest trades
\end{itemize}

\subsection{Administrator}
Also referred to as an Admin, is the person in charge of managing the operation of their respective field. For instance, a League admin is in charge of maintaining league settings. 

\subsubsection{League Administrator}
Manages the leagues that they have created
\begin{itemize}
\item[--] Can set league to be public/private
\item[--] Set the rules for the league
\end{itemize}

\subsubsection{Site Administrator}
Manages the overall website
\begin{itemize}
\item[--] Ensure fair competition between leagues/players
\end{itemize}

\subsection{Database System}
Holds the information for the accounts of all users
\begin{itemize}
\item[--] Insert information as accounts are created
\item[--] Push data back to views about users/events
\item[--] Store new data about about users/events
\end{itemize}

\subsection{Financial API}
Gives the stocks in our database up to date prices
\begin{itemize}
\item[--] Fetch real world information and update our database accordingly
\end{itemize}

\subsection{Browser}
The middleman between user and system
\begin{itemize}
\item[--] Present data to the user
\item[--] Retrieve data from the user
\end{itemize}

\subsection{Yahoo! Finance}
The unit that knows about current financial statistics
\begin{itemize}
\item[--] Retrieve data about stocks
\end{itemize}

\subsection{Queueing System}
A subsystem for scheduling orders so as not to block user
interactions.
\begin{itemize}
\item[--] Place orders to be executed or canceled asynchronously
\item[--] Schedule events and mailings for system
\end{itemize}
