\chapter{Customer Statement of Requirements}

\section{Problem Statement}

The stock market, more specifically the New York Stock
Exchange(NYSE) and the Nasdaq play a pivotal role in the American
economy today. Both are signals of the strength of the private
sector and consumer confidence. It is thus no surprise that
more and more people want to be involved in these markets
and attempt to increase their own wealth.\\

There is however a barrier to entry for many people, both
young and old in participating.  That is why with Paramount
Investments League we are interested in a platform for interacting
with these markets and providing educational interfaces for
breaking down these barriers.  Users should be able to easily
register with the system and begin participating immediately.
They should be given an imaginary cash portfolio where they can
perform basic market orders such as buy and sell. These orders to
should mimic real market orders as closely as possible and should
include a brokers fee. More sophisticated market maneuvers should be
unlocked as the user progresses through an achievements ladder.\\

Paramount Investments League is geared towards a wide array
of audiences and expects a variety of users with varying knowledge
levels to participate. In order to maintain appeal amongst these
users the platform should provide rewards to users for acheiving
particular goals.  We would like to replicate the idea of
achievements or trophies similar to the Microsoft xBox and Sony
Playstation family of systems. These achievements can award users
with new abilities or additional cash to their portfolio as they rise
up the achievements ladder. Users should also be able to create leagues
to help further enhance the competitiveness of the game.\\

Leagues exist to allow multiple users to compete against a subset
of the global user base with individual league rules.  This allows leagues
to set particular goals in order to be declared the winner.  Leagues
will require a cash buy-in that will be pooled together and distributed
to the winner(s) as seen fit by the league creator. To help facilitate
these leagues, a leader board will be created for each individual league
such that users can see their progress. In addition to league leader boards,
mutliple global leaderboards will be available providing specific metrics
of comparison.\\

To help facilitate a better understanding of markets, market metrics
should be available to the user through news feeds of companies in
their portfolio, interactive charts, and a live ticker of current
trades happening on our platform. Users should be able to have granular
control of email and social media updates.\\

The entire experience should be unified across mobile, tablet, and the
desktop and combined with the above features provide an enthralling
core experience for users to learn about the stock market.\\
