\chapter{History of Work, Current Status, \& Future Work}

\section{History of Work}

Throughout the semester we completed several of our planned milestones in a
punctual, thorough, and consistent manner.\\

Our first planned milestone, completing the Report 1 Part 1 prior to 9
February 2014, was met on time. We continued to meet our report deadlines for
Report 1 Part 2 and the full, compiled Report 1 by 16 February 2014 and 23
February 2013, respectively. For the second report, we successfully met our
deadlines for Report 2 Part 1 (consisting of Sequence Diagrams, timing and
communication diagrams) and Report 2 Part 2 (consisting of Class Diagrams,
Interface, Architecture design, data structures, UI, tests and implementations)
on 2 March 2014 and 9 March 2014, respectively.\\

As we met our initial Report deadlines, we also simultaneously began work on the
initial build of \textit{The Paramount Investment League}. We began with
deploying our server environment, which took place between 22 February and 2
March 2014. While we were initially weighing our options between dedicated
virtual private server (VPS) on Digital Ocean and Heroku, we determined that
a dedicated virtual private server would better suit our needs and we
successfully deployed it by 2 March 2013. In this time, we also finalized
our plan for mockup-based views and the CSS/HTML plan.\\

Populating the server with Ubuntu 12.04.4, Play Framework, Twitter Bootstrap,
and other supporting software, however, took a longer than anticipated. This is
because we needed to not just deploy it to the live server, but also set up the
enviornment on our local machines so that we could develop and test our code
without running in production. We also documented all these details on our
github wiki, which will allow future developers a walkthrough for getting setup
with the project. This extended beyond our initial range of 1 March 2014 to 8
March 2013 and was completed by 13 March 2014.\\

We completed our full Report 2 deadline by 15 March 2014. After this point
we shifted gears and committed to having \textit{The Paramount Investmets
League} Alpha build prepared for Demo 1. In the days between 13 March 2014 and
28 March 2014 we met several of our objectives. The Yahoo! Finance API was
implemented, the MySQL database structure was deployed and populated. Our
routing plan was completed, our views theme were implemented, and we
successfully got users, and portfolios at a working state in which data could be
utilized between them in our routing structure.\\

Our biggest strength was establishing manageable goals that still built on
the strengths and failures of our predecessors. We chose a functional UI but
were not overly-ambitious with functionality, otherwise; this enabled us to meet
our goals in a punctual manner. We almost fully implemented our achievements
system with unlockable functionality features is.\\

\section{Current Status}

Currently, \textit{The Paramount Investments League} is a functioning web
application. We have an online version of our latest builds on the domain
http://192.241.248.22/ based on our Virtual Private server hosted on Digital
Ocean. It features working orders, leagues, portfolios, and user systems with a
fully-functional and responsive UI that can be used in tablets and phones in
addition to personal computer to be user friendly for anyone on a smart device.
Most core functionalities have been deployed and the current status is
debugging and optimizing our website to address orders in an asynchronous fashion
to maximize the efficiency of our application.\\

We have added graphs via Highcharts as well as leagues, improved pagination
support, enhanced the UI based on user feedback, increased the amount of
available achievements and will be able to demonstrate the ability to unlock
functionality as one becomes an experienced investor.\\

\section{Key Accomplishments}

\textit{The Paramount Investment League} unlocked the following achievements:\\

\begin{itemize}
\item{Play Framework application for core Web Application functionality}
\item{A barrier free site registration process through the use of OAuth}
\item{A responsive UI usable on smart devices based on our custom flat theme}
\item{A minimalistic and easy-to-use system for users, portfolios, and leagues}
\item{An implementation of highcharts that presentably showed line-graph data }
\end{itemize}

\textit{The Paramount Investment League} also satisfied the following user stories:\\

\begin{itemize}
\item{ST-1}
\item{ST-2}
\item{ST-3}
\item{ST-4}
\item{ST-5}
\item{ST-6}
\item{ST-7}
\item{ST-8}
\item{ST-10}
\item{ST-12}
\item{ST-13}
\item{ST-17}
\item{ST-22}
\end{itemize}

\textit{The Paramount Investment League} also implemented the following use cases:\\

\begin{itemize}
\item{UC-1}
\item{UC-2}
\item{UC-3}
\item{UC-4}
\item{UC-5}
\end{itemize}

\section{Future Work}

The final stretch for a release-build \textit{The Paramount Investments League}
would be an immersive tutorial system activating upon user registration. This
would have extensively took advantage of AJAX and is the most complex type of
functionality to deploy on a live version of \textit{The Paramount Investment
League}, hence it would have required careful, slow, and surgical-level
development. This was one of our major post-demonstration goals, but the
level of sophistication for a fully-functional live tutorial upon user
registration was highly impractical for the remaining time we had.\\

We also would like to add an asynchronous processing system for orders so that
we can support stop and limit options. This would be unlockable functionality
but requires someone with the appropriate domain knowledge so that we can
implement it as true-to-life as possible.\\

Finally, to maximize user retention, another future work goal would have been
to implement social media and e-mail notification options so users can be
reminded to check and update their portfolios and leagues on a regular basis. A
mailer system was intended, however, development on that particular item fell
in favor of achievemnets, which were implemented by the Alpha.\\

\newpage

\section{Project Management}

As this project evolved, our contributions and interactions became more
complex and intertwined. It would be impossible for us to break down the work
and contributions that each individual did. It is for these reasons that we
feel as a team it is safe to say that we equally contributed to the project
and therefore request that equal contributions be applied for all members of
this project.
