\chapter*{Summary Of Changes}

\begin{enumerate}

\item Our problem statement has been changed to more accurately reflect the view of the customer. That is, the problem statement now more accurately represents the needs and desires of the customer. Moreover, we have chosen to elaborate on a good deal of our details of execution and motivation for each design solution.

\item The glossary of terms has been updated to more properly cite resources and to provide a more clean, easy to understand resource for the crucial terms being used after. 

\item Relevant citations have been added in all areas of the document to give proper mention to any and all referenced items.

\item Figure 2.1 has been elaborated. We believe this will clarify any confusion regarding its presence and intention as well as relevance to the UI requirements.

\item Specific stakeholders have been identified, and supporting actors such as those in the administrator role have been elaborated and expanded upon.

\item Use case casual descriptions have been added. These represent a general, modest overview of the specifications of each use case, such as to provide a basic reference in addition to the fully dressed model.

\item Use case diagram has been remodeled for clarity and a detailed description has been added for it. 

\item Alternative scenarios for use cases have been added or updated where necessary. If not alternative use case was necessary, this was specified and reasoning was elaborated.

\item Preliminary design items have been revised. All headers and images have been updated to properly reflect true performance on the website. Further, the labeling of figures and document logistics have been updated.

\item Concept has been updated to illustrate specific necessity for certain items and illuminate design choices such as the DB connection. Diagram descriptions have been added and general theory and reasoning behind design implementation have been provided. 

\item Use case 3 contract has had a post-condition added.

\item Class diagrams and method signatures have been given descriptions. All methods and attributes have been clarified and the diagram has been properly digitized and revised to reflect most recent design.

\item New design patterns have been added and implemented to show updated, second half of the course design patterns.

\item Traceability matrix has been added in report 2. 

\item Report 2 user interface design and implementation has been added, revised, and updated to reflect most recent work on the software design. 

\end{enumerate}
